---
title: "Project 1"
output: pdf_document
date: "2024-09-30"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Question Formulation:
Identify a question you want to answer with the dataset provided. Since our data is a used cars dataset, a possible question could be: 
"What factors most influence the price of a used car?"

Exploratory Data Analysis (EDA)
```{r}
library(tidyverse)

used_cars <- read.csv("used_cars_data.csv")

summary(used_cars)

colSums(is.na(used_cars))

# 2. Distribution of Prices
ggplot(used_cars, aes(x = Price)) +
  geom_histogram(bins = 30, fill = "blue", alpha = 0.7) +
  labs(title = "Distribution of Car Prices", x = "Price", y = "Frequency")


# Car Price vs Year
plot(used_cars$Year, used_cars$Price, main = "Car Price vs Year", xlab = "Year", ylab = "Price(in thousand USD)")

```


2. Data Wrangling:
Load the data. Clean the data: handle missing values, filter irrelevant columns, and ensure the data types are correct. Subset the data if necessary. 
```{r}
# Data wrangling: Remove rows with missing values
used_cars_clean <- na.omit(used_cars)

# 3. Mileage vs Price
ggplot(used_cars, aes(x = Mileage, y = Price)) +
  geom_point(color = "darkgreen") +
  labs(title = "Mileage vs Price", x = "Mileage (kmpl)", y = "Price (in Lakhs)")

# 4. Fuel Type vs Price
ggplot(used_cars, aes(x = Fuel_Type, y = Price, fill = Fuel_Type)) +
  geom_boxplot() +
  labs(title = "Fuel Type vs Price", x = "Fuel Type", y = "Price (in Lakhs)")

# 5. Kilometers Driven vs Price
ggplot(used_cars, aes(x = Kilometers_Driven, y = Price)) +
  geom_point(color = "purple") +
  labs(title = "Kilometers Driven vs Price", x = "Kilometers Driven", y = "Price (in Lakhs)")

# 6. Transmission Type Distribution
ggplot(used_cars, aes(x = Transmission, fill = Transmission)) +
  geom_bar() +
  labs(title = "Transmission Type Distribution", x = "Transmission Type", y = "Count")

# 7. Power vs Price
ggplot(used_cars, aes(x = Power, y = Price)) +
  geom_point(color = "red") +
  labs(title = "Power vs Price", x = "Power (bhp)", y = "Price (in Lakhs)")

```
```{r}
# Data wrangling: Remove rows with missing values
used_cars_clean <- na.omit(used_cars)

ggplot(used_cars, aes(x = Fuel_Type, y = Price, fill = Fuel_Type)) +
  geom_jitter() +
  labs(title = "Fuel Type vs Price", x = "Fuel Type", y = "Price (in Lakhs)")
```


3. Visualizations:
Use at least two visualizations. For example, one can be a scatter plot showing price versus mileage, and another can be a boxplot showing price distribution by car brand or model.

4. Analysis:
Interpret the visualizations and run a linear regression or other statistical methods to explore relationships between variables.

```{r}
library(tidyverse)  
library(ggplot2)    

used_cars <- read.csv("used_cars_data.csv")

head(used_cars)
summary(used_cars)

# Data wrangling: Remove rows with missing values
used_cars_clean <- na.omit(used_cars)

# Check data structure
str(used_cars_clean)

# If needed, filter data (example: filter by specific columns or conditions)
# used_cars_filtered <- used_cars_clean %>% filter(Condition == "Good")

# Scatter plot: Price vs Mileage
ggplot(used_cars_clean, aes(x = Mileage, y = Price)) +
  geom_point() +
  labs(title = "Price vs Mileage", x = "Mileage", y = "Price")

# Boxplot: Price distribution by brand
ggplot(used_cars_clean, aes(x = Name, y = Price)) +
  geom_boxplot() +
  labs(title = "Price Distribution by Brand", x = "Brand", y = "Price")

# Linear regression: Predicting price based on Mileage and other factors
model <- lm(Price ~ Mileage + Name + Year, data = used_cars_clean)
summary(model)

```

